Instructions for ACL 2020 Proceedings

### 2019-12-05 reports/ACL2020 Paper/acl2020-paper.tex
add experiment 3 analysis

\paragraph{Fine-tuning and laughter}
Since the laughter token doesn't appear in the original BERT vocabulary, only fine-tuned models can meaningfully make use of laughter in utterance representations. 
This gives us another opportunity to assess whether laughter is useful in dialogue act recognition.
We find that although \%4.6 of utterances in SWDA contain laughter, \%7.3 of utterances misclassified by \texttt{BERT} but correctly classified by \texttt{BERT-FT} contain laughter, suggesting that the fine-tuned model utterance encoder is making use of laughter. 
For AMI-DA, the effect is less pronounced, but still present§: \%8.5 of utterances contain laughter, and \%9.6 of utterances where fine-tuning makes a difference contain laughter.

@@

References
\begin{itemize}
  \item \citet{austinHowThingsWords2009} -- speeh acts
  \item \citet{coreCodingDialogsDAMSL1997} -- DAMSL dialogue act tagging scheme. SWDA tags are based on this (I think AMI are too). Concept of multi-layer DA tags; forward/backward function
  \item \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a} -- SWBD-DAMSL coders manual
  \item \citet{devlinBERTPretrainingDeep2018} -- Original BERT paper
  \item \citet{sunHowFineTuneBERT2019} -- recommendations for fine-tuninig BERT
  \item \citet{mikolovDistributedRepresentationsWords2013} -- word2vec
  \item \citet{petersTuneNotTune2019} -- when and how to fine-tune pre-trained representations
  \item \citet{kimConvolutionalNeuralNetworks2014} -- CNN sentence representation
\end{itemize}

\section{Related work} % add references first
Dialogue act recoginition
\begin{itemize}
  \item \citet{pragstVectorRepresentationUtterances2018} -- dialogue vector models. Uses vector-manual DA tag correspondance to argue for semantic relevance of their vector models (related to how we use DA tagging to verrify BERT usefulness)
  \item \citet{cerisaraEffectsUsingWord2vec2017} -- standard pre-trained word embeddings do not help for DAR in any of three tested languages (English, French, Czech)
  \item \citet{kalchbrennerRecurrentConvolutionalNeural2013} -- DAR model similar to our architecture. Uses an RNN ``discourse model'' and a CNN similar to our baseline encoder
  \item \citet{stolckeDialogueActModeling2000} -- OG DAR model. Uses an HMM with various lexical and prosodic features
  \item \citet{khanpourDialogueActClassification2016} -- Deep LSTM utt representation. No notion of context. Finds word vectors are useful.
  \item \citet{tranPreservingDistributionalInformation2017} -- Sequential DA prediction with uncertainty propegation
  \item \citet{chenDialogueActRecognition2017} -- SOTA? SWDA DAR using attention and CRF over utterances
  \item \citet{ortegaNeuralbasedContextRepresentation2017} -- SWDA DAR with attention-based context representations and CNN utterance representations
  \item \citet{shenNeuralAttentionModels2016} -- Uses attention for utt encoding in DAR. No notion of context, I think.
  \item \citet{tranHierarchicalNeuralModel2017} -- RNNs at both the utteranec and dialogue level. Also attention. Very similar to our architecture.
\end{itemize}

@@

% - AMI, SWBD + comparison table % Bill
\begin{table}[]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Switchboard}       & \textbf{AMI Corpus}                     \\ \midrule
Dyadic                     & Multi-party                             \\
Casual conversation        & Mock business meeting                   \\
Telephone                  & In-person \& video                      \\ \midrule
English                    & English                                 \\ 
Native speakers            & Native \& non-native speakers           \\ 
early '90s                 & 2000s                                   \\ \midrule
2200 conversations         & 171 meetings                            \\
  \hspace{1em} 1155 in SWDA               & \hspace{1em} 139 in AMI-DA                           \\
400 utterances             & 118k utterances                         \\
3M tokens                  & 1.2M tokens                             \\ \bottomrule
\end{tabular}
  \caption{Comparison between Switchboard and the AMI Meeting Corpus}
  \label{table:corpora}
\end{table}

@@

Our DAR model has two components: an utterance encoder, and a sequence model that predicts the dialogue act tag (figure \ref{fig:model-architecture}).
Since we are primarily interested in comparing different utterance encoders, we use a simple RNN as the sequence model in every configuration. 
The RNN takes the encoded utterance as input at each time step
Its hidden state is passed to a simple linear classification layer over dilague act tags.
Conceptually, the encoded utterance represents the context-agnostic semantic content of the utterance, and the hidden state of the RNN represents the discourse context.

@@

\section{Experiments}
\subsection{Experiment 1: Impact of laughter}   % Vlad
In the first experiment we investigated whether laughter, as an example of a dialogue-specific signal, is a helpful feature for DAR.
Therefore, we train another version of each model: one containing laughters (L) and with laughters left out (NL), and compare their performances in DAR task.

@@

\subsection{Experiment 2: Impact of pre-training} % Bill
% - compare i) pre-trained BERT with freezing ii) pretrained with no freezing iii) randolmly initialized
Next, we take a direct look at how pre-training affects BERT's performance as an utterance encoder for our DAR model.
In particular, we consider the performance of DAR models with three different utterance encoders:
\begin{itemize}
  \item \texttt{BERT} -- pre-trained BERT without fine-tuning (frozen during DAR training)
  \item \texttt{BERT-FT} -- pre-trained BERT with fine-tuninig 
  \item \texttt{BERT-RI} -- randomly initialized BERT with fine-tuning 
\end{itemize}

\begin{table}[]
\centering 
\begin{tabular}{@{}lll@{}}
\toprule
                 & SWDA  & AMI-DA \\ \midrule
\texttt{BERT}       & 55.61 & 46.59  \\
\texttt{BERT-FT}    & 76.93 & 66.94  \\
\texttt{BERT-RI}    & 73.80 & 61.53  
\end{tabular}
  \caption{Micro-average DAR accuracy}
  \label{table:exp2-avg}
\end{table}

@@

To help answer these questions, we compare accuracy results of the above three models by dialogue act tag.

@@

\subsection{Experiment 3: Impact of dialogue pre-training} % Bill
% - pre-train AMI+SWBD -> train SWDA/AMI-DA -> test SWDA/AMI-DA
% - pre-traing tasks: 1) next utterance, 2) masked token, 3) both ?
% - compare frozen with no dialogue pre-training vs pre-trained on dialogue w.r.t. L/NL (same as in Experiment 1)
\begin{itemize}
  \item Setup
    \begin{itemize}
      \item we do additional pre-training for the BERT encoder on in-domain data
      \item note: this is sometimes referred to as fine-tuning, but we reserve that term for task-specific training of the encoder model

@@

\subsection{Experiment 4: Cross-domain pre-training (if time permits)} % Bill
%  - cross-domain pre-training

\section{Discussion} % add items to discuss
\begin{itemize}
  \item RoBERTa training scheme finds that next sentence prediction is of little importance. Is this true for us too? (suspect not due to discourse importance). see: https://github.com/huggingface/transformers/issues/1622
\end{itemize}

>>>>

\paragraph{Contributions}
The main results of this paper have to do with to the usefulness of language model fine-tuning for DAR, 
the impact of laughter on DAR, and the relationship between the two.
\begin{itemize}
  \item Laughter is useful for dialogue act recoginition (\S\ref{sec:experiment1}).
  \item The impact of laughter is different for different dialogue acts. [Bigger for forward/backward?] (\S\ref{sec:experiment1})
  \item Standard BERT pre-traininig is useful for DAR, but the impact of pre-training is smaller than than of fine-tuning (\S\ref{sec:experiment2})
  \item 
\end{itemize}

@@

References
\begin{itemize}
  \item \citet{austinHowThingsWords2009} -- speeh acts
  \item \citet{coreCodingDialogsDAMSL1997} -- DAMSL dialogue act tagging scheme. SWDA tags are based on this (I think AMI are too). Concept of multi-layer DA tags; forward/backward function
  \item \citet{jurafskySwitchboardSWBDDAMSLShallowDiscourseFunction1997a} -- SWBD-DAMSL coders manual
  \item \citet{devlinBERTPretrainingDeep2018} -- Original BERT paper
  \item \citet{sunHowFineTuneBERT2019} -- recommendations for fine-tuninig BERT
  \item \citet{mikolovDistributedRepresentationsWords2013} -- word2vec
  \item \citet{petersTuneNotTune2019} -- when and how to fine-tune pre-trained representations
  \item \citet{kimConvolutionalNeuralNetworks2014} -- CNN sentence representation
  \item \citet{stolckeDialogueActModeling2000} -- OG DAR model. Uses an HMM with various lexical and prosodic features
\end{itemize}

\section{Related work} % add references first
Dialogue act recoginition
\begin{itemize}
  \item \citet{pragstVectorRepresentationUtterances2018} -- dialogue vector models. Uses vector-manual DA tag correspondance to argue for semantic relevance of their vector models (related to how we use DA tagging to verrify BERT usefulness)
  \item \citet{cerisaraEffectsUsingWord2vec2017} -- standard pre-trained word embeddings do not help for DAR in any of three tested languages (English, French, Czech)
  \item \citet{kalchbrennerRecurrentConvolutionalNeural2013} -- DAR model similar to our architecture. Uses an RNN ``discourse model'' and a CNN similar to our baseline encoder
  \item \citet{khanpourDialogueActClassification2016} -- Deep LSTM utt representation. No notion of context. Finds word vectors are useful.
  \item \citet{tranPreservingDistributionalInformation2017} -- Sequential DA prediction with uncertainty propegation
  \item \citet{chenDialogueActRecognition2017} -- SOTA? SWDA DAR using attention and CRF over utterances
  \item \citet{ortegaNeuralbasedContextRepresentation2017} -- SWDA DAR with attention-based context representations and CNN utterance representations
  \item \citet{shenNeuralAttentionModels2016} -- Uses attention for utt encoding in DAR. No notion of context, I think.
  \item \citet{tranHierarchicalNeuralModel2017} -- RNNs at both the utteranec and dialogue level. Also attention. Very similar to our architecture.
\end{itemize}

@@

% - AMI, SWBD + comparison table % Bill
\begin{table}[]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Switchboard}       & \textbf{AMI Corpus}                     \\ \midrule
Dyadic                     & Multi-party                             \\
Casual conversation        & Mock business meeting                   \\
Telephone                  & In-person \& video                      \\ \midrule
English                    & English                                 \\ 
Native speakers            & Native \& non-native speakers           \\ 
early '90s                 & 2000s                                   \\ \midrule
2200 conversations         & 171 meetings                            \\
  \hspace{1em} 1155 in SWDA               & \hspace{1em} 139 in AMI-DA                           \\
400k utterances             & 118k utterances                         \\
3M tokens                  & 1.2M tokens                             \\ \bottomrule
\end{tabular}
  \caption{Comparison between Switchboard and the AMI Meeting Corpus}
  \label{table:corpora}
\end{table}

@@

We employ a simple DAR model with two components: an encoder that vectorizes utterances, and a sequence model that predicts dialogue act tags from the vectorized utterances (figure \ref{fig:model-architecture}).
Since we are primarily interested in comparing different utterance encoders, we use a simple RNN as the sequence model in every configuration. 
The RNN takes the encoded utterance as input at each time step
Its hidden state is passed to a simple linear classification layer over dilague act tags.
Conceptually, the encoded utterance represents the context-agnostic semantic content of the utterance, and the hidden state of the RNN represents the discourse context.

As a baseline utterance encoder, we use a word-level CNN with window sizes of 3, 4, and 5, each with 100 feature maps \citep{kimConvolutionalNeuralNetworks2014}. 
The model uses 100-dimensional word embeddings, which are initialized with pre-trained gloVe vectors in some configurations \citep{penningtonGloveGlobalVectors2014}.

For the BERT utterance encoder, we use the BERT-BASE model with hidden size of 768 and 12 transformer layers and self-attention heads \citep[][see \S3.1]{devlinBERTPretrainingDeep2018}.
We use the un-cased model implemenetd by \citet{wolfHuggingFaceTransformersStateoftheart2019}.

@@

\section{Experiments}
\subsection{Experiment 1: Impact of laughter} \label{sec:experiment1}   % Vlad
In the first experiment we investigated whether laughter, as an example of a dialogue-specific signal, is a helpful feature for DAR.
Therefore, we train another version of each model: one containing laughters (L) and with laughters left out (NL), and compare their performances in DAR task.

@@

\subsection{Experiment 2: Impact of pre-training vs. fine-tuning} \label{sec:experiment2} % Bill
% - compare i) pre-trained BERT with freezing ii) pretrained with no freezing iii) randolmly initialized
Next, we take a direct look at how pre-training affects BERT's performance as an utterance encoder for our DAR model.
In particular, we consider the performance of DAR models with three different utterance encoders:
\begin{itemize}
  \item \texttt{BERT} -- pre-trained BERT without fine-tuning 
  \item \texttt{BERT-FT} -- pre-trained BERT with DAR fine-tuninig 
  \item \texttt{BERT-RI} -- randomly initialized BERT with dAR fine-tuning 
\end{itemize}

\begin{table}[]
\centering 
\begin{tabular}{@{}lll@{}}
\toprule
                 & SWDA  & AMI-DA \\ \midrule
\texttt{BERT}       & 55.61 & 46.59  \\
\texttt{BERT-FT}    & 76.93 & 66.94  \\
\texttt{BERT-RI}    & 73.80 & 61.53  
\end{tabular}
  \caption{Micro-average DAR recall}
  \label{table:exp2-avg}
\end{table}

@@

To help answer these questions, we compare performance of the above three models by dialogue act tag.

@@

\paragraph{Fine-tuning and laughter}
Since the laughter token doesn't appear in the original BERT vocabulary, only fine-tuned models can meaningfully make use of laughter in utterance representations. 
This gives us another opportunity to assess whether laughter is useful in dialogue act recognition.
We find that although \%4.6 of utterances in SWDA contain laughter, \%7.3 of utterances misclassified by \texttt{BERT} but correctly classified by \texttt{BERT-FT} contain laughter, suggesting that the fine-tuned encoder makes use of laughter. 
For AMI-DA, the effect is less pronounced, but still present§: \%8.5 of utterances contain laughter, and \%9.6 of utterances where fine-tuning makes a difference contain laughter.

\subsection{Experiment 3: Impact of in-domain pre-training} \label{sec:experiment3} % Bill
% - pre-train AMI+SWBD -> train SWDA/AMI-DA -> test SWDA/AMI-DA
% - pre-traing tasks: 1) next utterance, 2) masked token, 3) both ?
% - compare frozen with no dialogue pre-training vs pre-trained on dialogue w.r.t. L/NL (same as in Experiment 1)

Next, we assess the effect of in-domain pre-training of BERT's performance as an utterance encoder.\footnote{
In-domain pre-training is sometimes referred to as fine-tuning, but we reserve that term for task-specific training on labeled data.}
We construct pre-training corpora from the SWDA portion of the un-labelled Switchboard corpus and from the entire AMI corpus (including meetings with no human-annotated DA tags that are not included in the DAR training set).
In both cases, we exclude dialogues that are reserved for DAR testing.

We use the same pre-training task described by \citet{devlinBERTPretrainingDeep2018}, which combines masked token prediction and next sentence (utterance) detection. 
Distractor utterances are drawn at random from another dialogue in the corpus
and each epoch is generated separately so that different distractor sentences appear each time.
We then performed DAR fine-tuning and inference with the in-domain pre-trained BERT models just as before.

For AMI, in-domain pre-training offers a modest performance boost, but there is no discernable effect in the case of Switchboard.
Indeed, when BERT is frozen during fine-tuning, the model that received no additional pre-training performs better by more than 3 percentage points (table \ref{tab:exp3-recall}).

\begin{table}[]
\begin{tabular}{@{}lll@{}}
\toprule
                       & SWDA  & AMI-DA \\ \midrule
in-domain pre-training & 77.02 & 68.64  \\
no fine-tuning         & 52.30 & 48.05  \\ \midrule
standard pre-training  & 76.93 & 66.94  \\
no fine-tuniing        & 55.61 & 46.59  \\ \bottomrule
\end{tabular}
  \caption{Micro-average DAR recall for different pre-training schemas.}
  \label{tab:exp3-recall}
\end{table}

We found no discernable difference between pre-traininig on dialogues from the same corpus and pre-traininig on the combined corpus.
These results could be explained by the relatively small size of the dialogue corpora.

\begin{itemize}
  \item Setup
    \begin{itemize}
      \item we do additional pre-training for the BERT encoder on in-domain data
      \item note: this is sometimes referred to as fine-tuning, but we reserve that term for task-specific training of the encoder model

@@

\subsection{Experiment 4: Cross-domain pre-training (if time permits)} \label{sec:experiment4} % Bill
%  - cross-domain pre-training

\section{Discussion} % add items to discuss
\begin{itemize}
  \item RoBERTa training scheme finds that next sentence prediction is of little importance. Is this true for us too? (suspect not due to discourse importance). see: https://github.com/huggingface/transformers/issues/1622
  \item Issues related to working with transcribed speech: Different kinds of laughter are all represented by the same token. Does transcription orthography capture prosidy? We know prosidy is useful for DAR (Jurafsky).
\end{itemize}
